### 2021-09-14 paper/localpsf.tex
removed old stuff section from paper

\section{DISORGANIZED OLD STUFF}

\begin{proof}[Proof of Theorem \ref{alg:weighting_functions_incremental}]
	For notational convenience, in this proof we write $w$, $\lambda$, and $e$ instead of $w_i$, $\lambda_i$, and $e_i$, respectively. Here subscripts for $\lambda$, and $e$ instead denote components of those vectors. For example, here $\lambda_j$ denotes the $j^\text{th}$ component of the vector $\lambda$, which corresponds to the $j^\text{th}$ component of the vector $\lambda_i$ in Algorithm \ref{alg:weighting_functions_incremental}.

	From standard optimization theory, the solution to optimization problem \ref{eq:wi_optimization_problem} is the stationary point of the Lagrangian,
	\begin{equation*}
	\mathcal{L}(w,\lambda) = \frac{1}{2}\|\Delta w\|^2 + \sum_{j=1}^r \lambda_j\left(w(x_j) - e_j\right).
	\end{equation*}
	The plan of this proof is to show that $\nabla \mathcal{L}(w,\lambda)=0$, which will verify that $w$ solves optimization problem \ref{eq:wi_optimization_problem}.

	Using the definition of $w_i$ in \eqref{eq:definition_of_wi_alg}, we may write the gradient of $\mathcal{L}$ with respect to $\lambda_j$ as
	\begin{equation*}
	\nabla_{\lambda_j} \mathcal{L}(w, \lambda) = w(x_j) - e_j
	= \beta - \sum_{k=1}^r \lambda_k \secondgreens_k(x_j) - e_j.
	\end{equation*}
	Using Lemma \ref{lem:psi_delta_eval} with $h=\secondgreens_k$, the equation for $\secondgreens_k$ in \eqref{eq:theta_eq}, and the definition of $S$ in \eqref{eq:defn_of_S_alg}, we have
	\begin{align*}
	\sum_{k=1}^r \lambda_k \secondgreens_k(x_j) &= \sum_{k=1}^r \lambda_k \left(\firstgreens_j, \Delta \secondgreens_k\right)_{L^2(\Omega)}\\
	&= \sum_{k=1}^r \lambda_k \left(\firstgreens_j, \firstgreens_k\right)_{L^2(\Omega)} = \left(S \lambda\right)_j.
	\end{align*}
	Combining all of these components of $\nabla_\lambda \mathcal{L}$ into a single vector and using the definition of $\lambda$ in \eqref{eq:definition_of_mu_alg} yields
	\begin{align*}
	\nabla_\lambda \mathcal{L}(w, \lambda) &= \beta \mathbf{1} - e - S \lambda \\
	&= \beta \mathbf{1} - e - S \left(-S^{-1}\left(e - \beta \mathbf{1}\right)\right) = 0.
	\end{align*}

	Taking the directional derivative of $\mathcal{L}$ with respect to $w$ in direction $h$ and using Lemma \ref{lem:psi_delta_eval} yields
	\begin{align}
	\nabla_w \mathcal{L}(w, \lambda)h &= \left(\Delta w, \Delta h\right)_{L^2(\Omega)} + \sum_{j=1}^r \lambda_j h(x_j) \nonumber \\
	&= \left(\Delta w, \Delta h\right)_{L^2(\Omega)} + \sum_{j=1}^r \lambda_j \left(\firstgreens_j, \Delta h\right)_{L^2(\Omega)} + \lambda_j \avg(h) \nonumber \\
	&= \left(\Delta w + \sum_{j=1}^r \lambda_j \firstgreens_j,~ \Delta h\right)_{L^2(\Omega)} + \avg(h) \mathbf{1}^T \lambda. \label{eq:L_w_38}
	\end{align}
	Using the definition of $w$ in Algorithm \ref{alg:weighting_functions_incremental}, and the fact that the Laplacian of a constant function is zero, we have
	\begin{equation*}
	\Delta w = -\sum_{j=1}^r \lambda_j \Delta \secondgreens_j 
	= -\sum_{j=1}^r \lambda_j \firstgreens_j,
	\end{equation*}
	which implies that the first term in \eqref{eq:L_w_38} is zero. By the definition of $\lambda$ in \eqref{eq:definition_of_mu_alg} and $\beta$ in \eqref{eq:definition_of_alpha_alg}, we have
	\begin{align*}
	\mathbf{1}^T \lambda &= -\mathbf{1}^T S^{-1} \left(e - \beta \mathbf{1}\right) \\
	&= -\mathbf{1}^T S^{-1} e + \beta \mathbf{1}^T S^{-1} \mathbf{1} \\
	&= -\mathbf{1}^T S^{-1} e + \frac{\mathbf{1}^T S^{-1} e}{\mathbf{1}^T S^{-1} \mathbf{1}} \mathbf{1}^T S^{-1} \mathbf{1} = 0,
	\end{align*}
	which implies that the second term in \eqref{eq:L_w_38} is zero. Thus $\nabla_w \mathcal{L}(w, \lambda) = 0$, so Algorithm \ref{alg:weighting_functions_incremental} produces the solution to optimization problem \ref{eq:wi_optimization_problem}.
\end{proof}

\begin{defn}[Weighting function optimization problem]
	Let $\Omega \subset \mathbb{R}^d$, $d\in\{1,2,3\}$, be an open bounded domain with, let $x_i \in \Omega$ for $i=1,\dots,r$, and let $f \in \mathbb{R}^r$. We consider the optimization problem
	\begin{equation}
	\label{eq:generic_optimization_initial}
	\begin{aligned}
	\min_{\gamma \in H^2_N(\Omega)} &\quad \frac{1}{2}\norm{\Delta \gamma}_{L^2(\Omega)}^2 \\
	\text{such that} &\quad \gamma(x_i) = f_i, \quad i=1,\dots,r.
	\end{aligned}
	\end{equation}
	A minimizer, $\gamma^*$, of \eqref{eq:generic_optimization_initial} is a function defined on $\Omega$ that interpolates the data pairs $(x_i,f_i)$, and is as flat as possible in a least squares sense. 
	We denote the objective function for optimization problem \eqref{eq:generic_optimization_initial} by 
	\begin{equation}
	\label{eq:wi_objective}
	J(\gamma) := \frac{1}{2}||\Delta \gamma||^2_{L^2(\Omega)}.
	\end{equation}
	We denote the feasible set for optimization problem \eqref{eq:generic_optimization_initial} by 
	\begin{equation}
	\label{eq:wi_feasible_set}
	X := \{u \in H^2_N : u(x_i)=f_i~\text{for}~ i=1,\dots,r\}.
	\end{equation}
	We denote the tangent space to the feasible set by
	\begin{equation}
	\label{eq:wi_tangent_space}
	X_0 := \{u \in H^2_N : u(x_i)=0~\text{for}~ i=1,\dots,r\}.
	\end{equation}
\end{defn}

\begin{lem}[Elliptic regularity on $X_0$]
	\label{lem:elliptic_regularity_x0}
	If $\partial \Omega$ is $C^{1,1}$, then there exists a constant $C > 0$ such that
	\begin{equation*}
	||u||_{H^2(\Omega)} \le C ||\Delta u||_{L^2(\Omega)}
	\end{equation*}
	for all $u \in X_0$.
\end{lem}

\begin{proof}
	Let $\widetilde{u}$ be version of $u$ that has been shifted up or down by a constant such that $\int_\Omega \overline{u} = 0$. We have
	\begin{align*}
	||D^1 u||_{\left(L^2(\Omega)\right)^d}^2 + ||D^2 u||_{\left(L^2(\Omega)\right)^{d \times d}}^2 &= ||D^1 \widetilde{u}||_{\left(L^2(\Omega)\right)^d}^2 + ||D^2 \widetilde{u}||_{\left(L^2(\Omega)\right)^{d \times d}}^2\\
	&\le ||\widetilde{u}||_{H^2(\Omega)}^2 \\
	&\le C_1 ||\Delta \widetilde{u}||_{L^2(\Omega)}^2 \\
	&= C_1 ||\Delta u||_{L^2(\Omega)}^2
	\end{align*}
	for some constant $C_1$. In the first and fourth lines we used the fact that the derivative of a constant is zero, in the second line we used the definition of the $H^2$ norm, and in the third line we used the standard elliptic regularity result for pure Neumann problems (see, e.g., Theorem 8.13 (b) in \cite{Arbogast}).

	To complete the proof, we will now show that there exists a constant $C_2$ such that $||u||_{L^2(\Omega)}^2 \le C_2 ||\Delta u||_{L^2(\Omega)}^2$ for all $u \in X_0$. For this, we use a standard compactness argument, which closely follows the proof of Theorem 8.12 in \cite{ARBOGAST}. Suppose for the sake of contradiction that this result does not hold. Then there exists a sequence $\{u_k\}_{k=1}^\infty \subset X_0$ such that
	$||u_k||_{L^2(\Omega)}=1$ and $||\Delta u_k||_{L^2(\Omega)} \le 1/k$.
	By the result already proven, the sequence $u_k$ is bounded in $H^2(\Omega)$ as follows:
	\begin{align*}
	||u_k||_{H^2(\Omega)}^2 &= ||u_k||_{L^2(\Omega)}^2 + ||D^1 u||_{\left(L^2(\Omega)\right)^d}^2 + ||D^2 u||_{\left(L^2(\Omega)\right)^{d \times d}}^2 \\
	&\le ||u_k||_{L^2(\Omega)}^2 + C_1 ||\Delta u||_{L^2(\Omega)}^2 \le 1 + C_1.
	\end{align*}
	Therefore, by the Banach-Alaoglu theorem, there exists a subsequence $u_{k_j}$ and function $u \in X_0$ such that
	\begin{equation*}
	u_{k_j} \overset{w}{\rightharpoonup} u \quad \text{weakly in }H^2(\Omega).
	\end{equation*}
	Let $f \in L^2(\Omega)$. By the Cauchy-Schwarz inequality, the linear functional $v \mapsto \int_\Omega f(x) \Delta v(x) dx$ is bounded in $H^2(\Omega)$, and is therefore an element of $\left(H^2(\Omega)\right)^*$. Weak convergence therefore implies
	\begin{equation*}
	\int_\Omega f(x) \Delta u_k(x) dx \rightarrow \int_\Omega f(x) \Delta u(x) dx.
	\end{equation*}
	By the assumption $||\Delta u_k||_{L^2(\Omega)} \le 1/k$ and Cauchy-Schwarz, we also have 
	\begin{equation*}
	\int_\Omega f(x) \Delta u_k(x) dx \rightarrow 0,
	\end{equation*}
	so we must have
	\begin{equation*}
	\int_\Omega f(x) \Delta u(x) dx = 0.
	\end{equation*}
	Since this holds for all $f \in L^2(\Omega)$, by the fundamental lemma of the calculus of variations, $\Delta u(x) = 0$ almost everywhere in $\Omega$. This, combined with the fact that $u$ has Neumann zero boundary conditions, implies that $u$ is a constant function. Since $u$ has value zero at least one point in each connected component of $\Omega$, we have $u=0$. Note that pointwise values of $u$ are well-defined since the Sobolev embedding theorem imples that $H^2(\Omega)$ is continuously imbedded in the space of continuous functions $C^0(\Omega)$ when $d < 4$, and we are considering $d \in \{1,2,3\}$ (see, e.g., Theorem 7.19 in \cite{Arbogast}).

	On the other hand, by the Rellich-Kondrachov theorem, $H^2(\Omega)$ is compactly imbedded in $L^2(\Omega)$, so there must exist a sub-sub-sequence, $u_{k_{j_i}}$ such that 
	\begin{equation*}
	u_{k_{j_i}} \rightarrow u
	\end{equation*}
	strongly in $L^2(\Omega)$. By assumption $||u_{k_{j_i}}||_{L^2(\Omega)}=1$, so $||u||_{L^2(\Omega)}=1$. This contradicts the result $u=0$ that we previously derived, so we must conclude that there exists a constant $C_2 > 0$ such that
	\begin{equation*}
	||u||_{L^2(\Omega)} \le C_2 ||\Delta u||_{L^2(\Omega)}.
	\end{equation*}
	for all $u \in X_0$. Combining this with out previous result, we have
	\begin{equation*}
	||u||^2_{H^2(\Omega)} \le (C_1 + C_2)||\Delta u||^2
	\end{equation*}
	for all $u \in X_0$, which completes the proof.
\end{proof}

\begin{lem}[Well-posedness of weighting function optimization problem]
	\label{lem:wi_existence_and_uniqueness}
	There exists a unique solution to optimization problem \eqref{eq:generic_optimization_initial}.
\end{lem}

\begin{proof}
	By the Sobolev Imbedding Theorem (see, e.g., Theorem 7.20 in \cite{ARBOGAST}), $H^2_N(\Omega)$ is continuously imbedded in $C^0(\Omega)$, so pointwise evaluation $u \mapsto u(x_i)$ of functions at a point $x_i \in \Omega$ is a continuous linear functional on $H^2_N$. The set 
	\begin{equation}
	\label{eq:inverse_image_of_point}
	\{u \in H^2_N : u(x_i)=f_i\}
	\end{equation}
	is therefore a closed affine set in $H^2_N$, because it is the inverse image of a point under a continuous linear functional. Hence the feasible set $X$, defined in \eqref{eq:wi_feasible_set}, is a closed affine set in $H^2_N$, because it is the intersection of the sets in \eqref{eq:inverse_image_of_point} for $i=1,\dots,r$.

	The feasible set $X$ is convex because it is affine, and it is non-empty because interpolating the data pairs $\{(x_i, f_i)\}_{i=1}^r$ using any smooth interpolation method yields an element of $X$. Furthermore, the objective function, 
	\begin{equation}
	J(\gamma) := \frac{1}{2}||\Delta \gamma||^2_{L^2(\Omega)},
	\end{equation}
	is convex because it is the composition of a convex function with a linear map. Furthermore, the elliptic regularity result in Lemma \ref{lem:elliptic_regularity_x0} implies
	\begin{equation*}
	J''(\gamma)v^2 = ||\Delta v||^2_{L^2(\Omega)} \ge C ||v||_{H^2(\Omega)}^2
	\end{equation*}
	for all $v \in X_0$, which implies that $J$ is strongly convex on $X$.
\end{proof}

\begin{defn}
	\label{def:stiffness_mass}
	We define $\mathcal{K}:H^2(\Omega)\rightarrow L^2(\Omega)'$ and $\mathcal{M}:L^2(\Omega) \rightarrow L^2(\Omega)'$ to be the following linear operators:
	\begin{align*}
	\left(\mathcal{K}u\right)(v) :=& \int_\Omega v \Delta u ~dx \\
	\left(\mathcal{M}u\right)(v) :=& \int_\Omega u v ~dx,
	\end{align*}
	and $\mathcal{P}:H^2(\Omega)\rightarrow \mathbb{R}^r$ to be the following pointwise observation operator:
	\begin{equation*}
	(\mathcal{P}u)_i = u(x_i)
	\end{equation*}
	for $i=1,\dots,r$.
\end{defn}

\begin{prop}
	\label{prop:solution_operator_is_linear}
	Let $f \in \mathbb{R}^r$ be arbitrary. The optimization problem
	\begin{equation}
	\label{eq:generic_optimization_initial_old}
	\begin{aligned}
	\min_{u \in H^2(\Omega)} &\quad \frac{1}{2}\norm{\Delta u}_{L^2(\Omega)}^2 \\
	\text{such that} &\quad u(x_i) = f_i, \quad i=1,\dots,r
	\end{aligned}
	\end{equation}
	may be rewritten as follows:
	\begin{equation}
	\label{eq:generic_optimization}
	\begin{aligned}
	\min_{u \in H^2(\Omega)} &\quad \frac{1}{2} \left(\mathcal{K}^T\mathcal{M}^{-1}\mathcal{K}u\right)(u) \\
	\text{such that} &\quad 
	\mathcal{P} u = f.
	\end{aligned}
	\end{equation}
\end{prop}

\begin{prop}
	There exists a unique solution to optimization problem \eqref{eq:generic_optimization}. The solution to \eqref{eq:generic_optimization}, $u^*$, and the adjoint variable for enforcing the constraint, $\lambda^*$, solve the following Karun-Kush-Tucker (KKT) system:
	\begin{equation}
	\label{eq:weighting_kkt}
	\begin{bmatrix}
	\mathcal{K}^T\mathcal{M}^{-1}\mathcal{K} & \mathcal{P}^T \\
	\mathcal{P} & 0
	\end{bmatrix}
	\begin{bmatrix}
	u^* \\ \lambda^*
	\end{bmatrix}
	=
	\begin{bmatrix}
	0 \\ f
	\end{bmatrix},
	\end{equation}
	where we use block-matrix notation to denote block-operators.
\end{prop}

\begin{cor}
	\label{cor:linearity_of_solution_operator}
	Let $\mathcal{T}:\mathbb{R}^r \rightarrow H^2(\Omega)$ denote the solution operator for optimization problem \eqref{eq:generic_optimization}	as a function of $f$. That is, 
	\begin{equation*}
	\mathcal{T}(f) := u^*,
	\end{equation*}
	where $u^*$ is the minimizer of \eqref{eq:generic_optimization}. The operator $\mathcal{T}$ is a linear operator.
\end{cor}

\footnote{The reason for this dependence on spatial dimension is related to the fact that the fundamental solution of the biharmonic equation is continuous in $3$ or less dimensions, but singular in $4$ or more dimensions. In the unusual scenario where one is inverting for a parameter field in $4$ or more spatial dimensions, one could use a modified Poisson interpolation where $\Delta$ is replaced with $\Delta^\alpha$ in the objective function of \eqref{eq:wi_optimization_problem}, where $\alpha>1$ is chosen so that the fundamental solution of $\Delta^{2\alpha}$ is continuous.}

The \emph{point spread function} (PSF) of $\mathcal{A}$ at $x\in \Omega$ is
\begin{equation*}
\varphi_x(y) := \langle \mathcal{A},\delta_x\rangle^*(y+x) = A(y+x,x).
\end{equation*}
Here $\langle \mathcal{A}, \delta_x \rangle \in L^2(\Omega)'$ is the result of applying $\mathcal{A}$ to a point source $\delta_x$ (delta distribution) centered at $x$, and $\langle\mathcal{A},\delta_x\rangle^* \in L^2(\Omega)$ is the Riesz representation of $\langle\mathcal{A},\delta_x\rangle$. The PSF, $\varphi_x$, is the result of translating $\langle\mathcal{A},\delta_x\rangle^*$ to re-center it at zero instead of $x$. Recall the Riesz representation of a linear functional $\psi \in L^2(\Omega)'$ is the unique vector $\psi^* \in L^2(\Omega)$ satisfying $\left(\psi^*, v\right)_{L^2(\Omega)} = \psi(v)$ for all $v \in \L^2(\Omega)$.

The approximation $\widetilde{A}(y,x)$ may not be accurate if both $x$ and $y$ are near the boundary. Other approximation methods, if available, should be considered for the block of the operator associated with boundary-boundary interactions. Nevertheless, in our numerical results we see that approximation works well for the the inverse problem considered, without any modifications to the boundary-boundary block.

The solution to this system of equations is found by the following process:
\begin{enumerate}
	\item Compute 
	\begin{equation*}
	\Psi := K^+ E^T
	\end{equation*}
	by solving Neumann poisson problems for point source right hand sides, with point sources located at the points $x_i$, $i=1,\dots,q$.
	\item Compute 
	\begin{equation*}
	\Theta := K^+ M \Psi
	\end{equation*}
	by solving Neumann Poisson problems with the columns of $\Psi$ as distributed sources.
	\item Form 
	\begin{equation*}
	S = \Psi^T M \Psi
	\end{equation*}.
	\item Compute \begin{equation*}
	\alpha = \left(\mathbf{1}^T S^{-1} \mathbf{1}\right)^{-1}\mathbf{1}^T S^{-1} \mathbf{y}.
	\end{equation*}
	\item Compute 
	\begin{equation*}
	\boldsymbol{\lambda} = -S^{-1} \left(\mathbf{y} - \alpha \mathbf{1} \right).
	\end{equation*}
	\item Compute
	\begin{equation*}
	\mathbf{u} = -\Theta \boldsymbol{\lambda} + \alpha \mathbf{c}
	\end{equation*}
\end{enumerate}

Consider the Pine island glacier geometry shown in Figure REF. Regions of the glacier are separated by thin inlets of ocean. With radial basis function interpolation, points on one side of the inlet inappropriately influence the interpolation on the other side of the inlet. With Poisson interpolation, the PSF samples only influence the interpolation on their own side of the inlet.

\subsection{Computation of Poisson weighting functions}
\label{sec:computation_of_weighting_functions}

After discretization, optimization problem \eqref{eq:wi_optimization_problem} becomes
\begin{equation}
\label{eq:discrete_poisson_optimization_1}
\begin{aligned}
\min_{\mathbf{w}} &\quad \frac{1}{2}\mathbf{w}^T K^T M^{-1} K \mathbf{w} \\
\text{such that} &\quad E \mathbf{w} = \mathbf{d}.
\end{aligned}
\end{equation}
Here $\mathbf{w}$ is the discretization of $w_i$, $K$ is the stiffness matrix for the discretized Poisson problem with pure Neumann boundary conditions, $M$ is the mass matrix, and $\mathbf{d}=(0,\dots,0,1,0,\dots,0)$ is the length-$q$ vector with $i^\text{th}$ entry one and all other entries zero. Furthermore, $E$ is the pointwise observation matrix defined by $\left(E\mathbf{u}\right)_j = u(x_j)$, where $u$ denotes the function represented by the vector $\mathbf{u}$. Here we dropped the subscripts $i$ from variables for notational convenience. One must solve $q$ optimization problems of the form \eqref{eq:discrete_poisson_optimization_1}; one for each $i=1,\dots,q$.

In the remainder of this section we will derive an efficient algorithm for solving \eqref{eq:discrete_poisson_optimization_1}. The algorithm (Algorithm REF) is based on explicit formula for the solution of \eqref{eq:discrete_poisson_optimization_1} which we present in Proposition \ref{prop:poisson_interpolation_formula}. The formulas in Proposition \ref{prop:poisson_interpolation_formula} rely on certain matrices that we define in Definition \ref{defn:poisson_interpolation_matrices}. The primary computational cost of the algorithm is the solution of Poisson problems with pure Neumann boundary conditions.

\begin{defn}
	\label{defn:poisson_interpolation_matrices}
	Let 
	\begin{align*}
	\Psi :=& K^+ E^T, \\
	\Theta :=& K^+ M \Psi \\
	S :=& \Psi^T M \Psi,
	\end{align*}
	where $K^+$ is the Moore-Penrose pseudoinverse of $K$. Further, let $\mathbf{c}$ dente the discretization of the constant function $c(x)=1$ on $\Omega$, and let $\mathbf{1}:=(1,\dots,1)$ denote the vector of length $q$ with all entries equal to one.
\end{defn}

\begin{remark}
	Computing $\mathbf{g} = K^+\mathbf{f}$ is equivalent to solving the discretized Poisson problem with $f$ as the right hand side source, with pure Neumann boundary conditions, and with the constraint that the solution has average value equal to zero. That is,
	\begin{equation}
	\label{eq:pure_neumann_poisson}
	\mathbf{g} = K^+ \mathbf{f} \quad \Leftrightarrow \quad 
	\begin{cases}
	\Delta g = f, & \text{in }\Omega,\\
	\nu \cdot \nabla g = 0, & \text{on }\partial \Omega,\\
	\int_\Omega g(x) dx = 0,
	\end{cases}
	\end{equation}
	where $\nu$ denotes the normal to the boundary.

	Hence, the $i^\text{th}$ column of $\Psi$ is the result of solving the discretized pure Neumann Poisson problem, with a point source at location $x_i$. The $i^\text{th}$ column of $\Theta$ is the result of solving the discretized pure Neumann Poisson problem with distributed source given by the $i^\text{th}$ column of $\Psi$.
\end{remark}

\begin{prop}
	\label{prop:poisson_interpolation_formula}
	The solution to optimization problem \eqref{eq:discrete_poisson_optimization_1} is given by
	\begin{equation*}
	\mathbf{w} = -\Theta \boldsymbol{\lambda} + \alpha \mathbf{c},
	\end{equation*}
	where
	\begin{align*}
	\alpha =& \left(\mathbf{1}^T S^{-1} \mathbf{1}\right)^{-1}\mathbf{1}^T S^{-1} \mathbf{d} \\
	\boldsymbol{\lambda} =& -S^{-1} \left(\mathbf{d} - \alpha \mathbf{1} \right). \\
	\end{align*}
\end{prop}

\begin{proof}
	Let
	\begin{equation*}
	v := \mathcal{K} w_i,
	\end{equation*}
	and for the remainder of this proof let $e := e_i$.
	Since the null-space of the Laplacian with pure Neumann boundary conditions is the set of all constant functions, we have
	\begin{equation}
	\label{eq:definition_of_w}
	w_i = \mathcal{K}^+ v + \alpha C
	\end{equation}
	for some scalar $\alpha$.

	Writing optimization problem \eqref{eq:wi_optimization_problem} in terms of $v$ and $\alpha$ instead of $w_i$ yields the following equivalent optimization problem:
	\begin{equation}
	\label{eq:discrete_poisson_optimization_2}
	\begin{aligned}
	\min_{v \in L^2(\Omega)', \alpha \in \mathbb{R}} &\quad \frac{1}{2} v\left(\mathcal{M}^{-1} v\right) \\
	\text{such that} &\quad \mathcal{P}\mathcal{K}^+ v + \alpha \mathbf{1} = e.
	\end{aligned}
	\end{equation}
	The Lagrangian for optimization problem \eqref{eq:discrete_poisson_optimization_2} is
	\begin{equation*}
	\mathcal{L} = \frac{1}{2}v\left( \mathcal{M}^{-1} v\right) + \lambda^T\left(\mathcal{P}\mathcal{K}^+ v + \alpha \mathbf{1} - e\right).
	\end{equation*}
	The solution to this optimization problem is the stationary point of the Lagrangian, i.e., the point at which the gradient of the Lagrangian is zero:
	\begin{equation*}
	0 = \nabla \mathcal{L} = 
	\begin{bmatrix}
	\nabla_{v} \mathcal{L} \\
	\nabla_{\lambda} \mathcal{L} \\
	\nabla_\alpha \mathcal{L}
	\end{bmatrix} 
	= \begin{bmatrix}
	\mathcal{M}^{-1} v + \left(\mathcal{K}^+\right)^T \mathcal{P}^T \lambda \\
	\mathcal{P}\mathcal{K}^+v + \alpha \mathbf{1} - e \\
	\mathbf{1}^T \lambda
	\end{bmatrix}.
	\end{equation*}
	This equation may be rewritten as the following block $3 \times 3$ linear system:
	\begin{equation*}
	\begin{bmatrix}
	\mathcal{M}^{-1} & \left(\mathcal{K}^+\right)^T \mathcal{P}^T & 0 \\
	\mathcal{P}\mathcal{K}^+ & 0 & \mathbf{1} \\
	0 & \mathbf{1}^T & 0
	\end{bmatrix}
	\begin{bmatrix}
	v \\ \lambda \\ \alpha
	\end{bmatrix}
	=
	\begin{bmatrix}
	0 \\ e \\ 0
	\end{bmatrix}.
	\end{equation*}
	Performing block Gaussian elimination on this system allows us to reduce the system to the following block triangular form
	\begin{equation*}
	\begin{bmatrix}
	\mathcal{M}^{-1} & \left(\mathcal{K}^+\right)^T \mathcal{P}^T & 0 \\
	& -S & \mathbf{1} \\
	0 & 0 & \mathbf{1}^T S^{-1} \mathbf{1}
	\end{bmatrix}
	\begin{bmatrix}
	v \\ \lambda \\ \alpha
	\end{bmatrix}
	=
	\begin{bmatrix}
	0 \\ e \\ \mathbf{1}^T S^{-1} e
	\end{bmatrix}
	\end{equation*}
	where we recall that $S := \Psi^T \mathcal{M} \Psi = \mathcal{P}\mathcal{K}^+ \mathcal{M} \left(\mathcal{K}^+\right)^T \mathcal{P}^T$. From this block triangular system, we read off the solution as:
	\begin{align*}
	\alpha =& \left(\mathbf{1}^T S^{-1} \mathbf{1}\right)^{-1}\mathbf{1}^T S^{-1} \mathbf{d} \\
	\boldsymbol{\lambda} =& -S^{-1} \left(\mathbf{d} - \alpha \mathbf{1} \right) \\
	\mathbf{v} =& -M K^+ E^T \boldsymbol{\lambda}
	\end{align*}
	Substituting these results into the definition of $\mathbf{w}$ in \eqref{eq:definition_of_w}, we have
	\begin{equation*}
	\mathbf{w} = -K^+ M K^+ E^T \boldsymbol{\lambda} + \alpha \mathbf{c} = -\Theta \boldsymbol{\lambda} + \alpha \mathbf{c},
	\end{equation*}
	as required.
\end{proof}

We now design an incremental algorithm for constructing interpolants $\mathbf{u}$, in which we can add points $x_i$ more efficiently. Let
\begin{align*}
\Psi :=& K^+ E^T \\
\Theta :=& K^+ M \Psi
\end{align*}
so that 
\begin{equation*}
S = \Psi^T M \Psi
\end{equation*}
and
\begin{equation*}
\mathbf{u} = -\Theta \boldsymbol{\lambda} + \alpha \mathbf{c}
\end{equation*}
The columns of $\Psi$ are the responses of $A^+$ to point sources (delta distributions) centered at the sample points $x_i$. The columns of $\Theta$ are the responses of $A^+M^{-1} A$ to these point sources. The matrices $\Psi$ and $\Theta$ may be constructed incrementally as new points are added.

\section*{Acknowledgments}
We thank J.J. Alger, Longfei Gao, and Rami Nammour for helpful discussions.

>>>>

\section*{Acknowledgments}
We thank J.J. Alger, Longfei Gao, Mathew Hu, and Rami Nammour for helpful discussions.
